\documentclass[11pt,letterpaper]{article}
\usepackage{fullpage,amsmath,amssymb,amsthm,graphicx,enumerate,float,mathtools}
\usepackage[english]{babel}
%\usepackage[ruled]{algorithm2e}

%%%%%%%%%% Start TeXmacs macros
\newcommand{\nocomma}{}
\newcommand{\tmem}[1]{{\em #1\/}}
\newenvironment{enumeratealpha}{\begin{enumerate}[a{\textup{)}}] }{\end{enumerate}}
\newenvironment{enumeratenumeric}{\begin{enumerate}[1.] }{\end{enumerate}}
\newenvironment{enumerateroman}{\begin{enumerate}[i.] }{\end{enumerate}}
\newenvironment{itemizedot}{\begin{itemize} \renewcommand{\labelitemi}{$\bullet$}\renewcommand{\labelitemii}{$\bullet$}\renewcommand{\labelitemiii}{$\bullet$}\renewcommand{\labelitemiv}{$\bullet$}}{\end{itemize}}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
%%%%%%%%%% End TeXmacs macros

%%%%%%%%%% Begin Custom macros
\newtheorem{remark}{Remark}
\floatstyle{ruled}
\newfloat{algorithm}{thp}{lop}
\floatname{algorithm}{Algorithm}
\newcommand{\namedalgorithm}[2]{
    \begin{algorithm*}[t]
    \caption{#1}
    #2
    \end{algorithm*}
}

\DeclarePairedDelimiter\ceil{\lceil}{\rceil}

\newcommand{\OMIC}{\ensuremath{\mathsf{OMIC}}}
\newcommand{\OMC}{\ensuremath{\mathsf{OMC}}}
\newcommand{\SMIC}{\ensuremath{\mathsf{SMIC}}}
%%%%%%%%% End Custom Macros

\clubpenalty=10000 
\widowpenalty = 10000 

\begin{document}

\title{A Generalized Byzantine Model}

\author{
    Wang Cheng~\protect\footnote{\'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne,Switzerland, cheng.wang@epfl.ch, +41 78 924 08 90.}
    \and
    Carole Delporte-Gallet~\protect\footnote{LIAFA-Universit\'{e} Paris-Diderot, Paris, France, cd@liafa.univ-paris-diderot.fr, +33 1 57 27 92 25.}
    \and
    Hugues Fauconnier~\protect\footnote{LIAFA-Universit\'{e} Paris-Diderot, Paris, France, hf@liafa.univ-paris-diderot.fr, +33 1 57 27 92 25.}
    \and
    Rachid Guerraoui~\protect\footnote{\'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne, Switzerland, rachid.guerraoui@epfl.ch, +41 21 693 52 72.}
    \and
    Anne-Marie Kermarrec~\protect\footnote{INRIA Rennes Bretagne-Atlantique, France, anne-marie.kermarrec@inria.fr, +33 2 99 84 25 98.}
}
\date{}

\maketitle

\begin{abstract}

The classical Byzantine model assumes that a process is either correct and obeys the protocol assigned to it, or is Byzantine and may  behave completely arbitrarily, sending corrupted messages to all processes during its entire execution. In this paper we generalize that model and consider that, in each communication step, some of the processes might send corrupted messages to a \tmem{subset} of the processes. This enables to capture more accurately  practical situations where
processes experience possibly temporary bugs in specific parts of their code. We present this model and prove bounds on the number of correct processes needed to solve the classical interactive consistency and consensus problems.

\end{abstract}

\vspace{4cm}
\begin{center}
\Large This paper is a regular submission.\\
\Large The paper is a student paper.
\end{center}

\newpage
\pagenumbering{arabic}\setcounter{page}{1}

\section{Introduction}

Pease, Shostak and Lamport were the first to introduce
the Byzantine model in their landmark
paper~\cite{lamport1982byzantine,pease1980reaching}.
In their model, a Byzantine process is defined as a process that can
arbitrarily deviate from the protocol assigned to it.
They proved that  agreement is achievable
with a fully connected network if and only if the number of Byzantine
processes is less than one third of the total number of
processes. Dolev extended this
result to general networks, in which the connectivity number is more than twice
the number of faulty processes \cite{dolev1982byzantine}.
The early work on Byzantine agreement
is well summarized in the survey by Fisher~{\cite{fischer1983consensus}}.

Many approaches have been proposed to circumvent the impossibility results of
\cite{fischer1985impossibility} in the Byzantine context.
The work presented in \cite{dwork1988consensus} introduced the concept
of partial synchrony: an intermediate model between
synchronous and asynchronous models, allowing some
limited periods of asynchrony. Partial synchrony is considered weak enough to model  real systems
while  strong enough to make Byzantine agreement solvable.
% possible while being more practical compared to synchrony.
Alternative approaches rely on randomized algorithms (e.g.
{\cite{braud2013fast,dwork1988fault,king2011load,rabin1983randomized}}).

Accounting for the fact that communication failures sometimes dominate
computation ones (due to high reliability of hardware and operating systems), other models
focus on communication failures (e.g.
~{\cite{perry1986distributed,schmid2002formally}}) and hybrid failures
(e.g.~{\cite{gong1998byzantine,lincoln1993formally}}). Such models
consider that the Byzantine components are the communication channels instead of 
(in addition to) the processes.
For instance, in \cite{santoro1989time,santoro2007agreement}, Santoro and Widmayer
showed that consensus cannot be achieved with $\ceil*{\frac{n}{2}}$
Byzantine communication faults. 
In the area of security, problems of secure communication and computation in the presence of Byzantine adversary and incomplete network \cite{dolev1982byzantine,franklin1998secure} have also received a lot of attention.
%
% There are models consider communication failures (e.g.
% {\cite{perry1986distributed,schmid2002formally}}) and hybrid failures
% (e.g. {\cite{gong1998byzantine,lincoln1993formally}}), since
% communication failures over computation are increasing important in modern
% distributed system due to high reliability of modern processes and robust
% operate system. When compared to component fault, the most significant feature
% of communication failures is dynamic. In the paper
% {\cite{santoro1989time,santoro2007agreement}}, Santoro and Widmayer
% showed that consensus cannot achieve with $\left[ \frac{n}{2} \right]$
% Byzantine communication faults.
% %Other round-based models have been studied by
%Charron-Bost and Schiper {\cite{charron2009heard}} (the heard-of model), and
%by Schimd et al. {\cite{biely2011synchronous}} (a comprehensive hybrid model).

% \subsection*{Motivation}
%In spite of many different models in the literature, the primitive failures
%they consider are Byzantine failure, communication failure and benign failure
%(e.g. omission failure, manifest failure, etc.).
In the classical Byzantine failure model, as well as in models with Byzantine communication channels, the notion of Byzantine failure is sustainable over time: the models consider that the processes (resp. the channels) are either Byzantine, or are correct for the entire duration of the computation. In fact, the Byzantine failure model encompasses two different situations: (1) A system attack where an adversary coordinates the behavior of several processes (resp. channels) in order to corrupt the system (e.g. denial of service attack); (2) Software or hardware bugs that lead one or several processes (resp. channels) to behave in an arbitrary manner.
We argue that
assumptions are fairly different in these two situations. Typically, under
attack, the set of Byzantine processes might indeed send corrupted messages systematically, possibly
with the sole purpose of corrupting the entire execution of the algorithm. In situations where processes misbehave due to bugs, the number of corrupted messages might vary over time. In this case, the Byzantine failure model as defined in \cite{lamport1982byzantine,pease1980reaching} can be viewed as too conservative. It assumes the worst: failures occur due to a malicious intent rather than simply arbitrary bugs located in specific parts of the code that might not be repeated.

The motivation of this work is to generalize the Byzantine failure model, accounting
for these differences and reconsider some of the theoretical impossibilities in
this light. We study our generalized Byzantine model in a synchronous context
of $n$
processes of which up to $m$ can be faulty. The processes can
communicate with each other directly through a complete network.
We assume that each faulty process (partially controlled by
the adversary) is associated with up to $d$ Byzantine communication
links. We call such a process the
{\tmem{$d$-faulty process}}.
%AMK:so the processes are just faulty and channels are Byzantine right?
These $d$ Byzantine links are \tmem{dynamic}: they may be
different in different communication rounds.
Note that if $d=n-1$, our generalized Byzantine model instantiates the classical Byzantine model. From the component failure model's view, our generalization is orthogonal to those of \cite{tseng2013iterative,santoro2007agreement,amitanand2003distributed}.
% Our model merges the advantages of the classical Byzantine model \cite{lamport1982byzantine} and the
 % communication failure model \cite{santoro2007agreement}, which enables it to tolerate $O(m d)$ 
% faulty links and to be dynamic meanwhile.


In this paper, we mainly focus on the case when $d<n$.
The most important feature in this case is that {\tmem{$d$-faulty}}
processes always send correct messages to some processes in the system,
which enables us for instance to solve the \tmem{interactive consistency} problem~\cite{fischer1983consensus}. This problem consists in devising an algorithm
that allows every process $p$ to decide a value for each process $q$,
such that: (1) If $p$ and $q$ are correct, then $p$ decides the
initial value of $q$. (2) All correct processes decide the same
value for each process. Somehow, $d<n$ implies that the local
computation of the processes is always correct and only the
communication links related to the faulty processes are partially
controlled by the adversary - during specific rounds.
In this sense,  we treat all the processes as
correct ones. (Except in Section 6 where we show how the model 
can easily encompass crash failures.) 
In this context {\tmem{interactive consistency}}
means that every process knows the initial value of every other
process by the end of the computation.
% As a remark, in a system with
% all correct processes one can use {\tmem{interactive consistency}} to
% discover the transmission failures inside the system, for one can know
% the precise state and communication of the whole system.

Here is a brief summarization of our results.
We first give the necessary and sufficient
conditions for reaching interactive consistency with oral and signed
messages (Table \ref{tab:results}). Our sufficiency proofs are constructive and the algorithms
we provide are deterministic, while the necessity proofs are based on a 
scenario argument. We also obtain a tight bound for reaching interactive
consistency in the case we also consider crash failures.
%We also give a non-trivial upper bound for reaching \tmem{binary consensus} in Section \ref{sec:consensus}.


\begin{table}[h]
\centering
\begin{tabular}{|c|c|}
\hline
Oral messages & $n> \max \{ 2m+d,2d+m \}$\\
\hline
Signed messages & $n>2d+m$\\
\hline
\end{tabular}
\caption{\label{tab:results}Necessary and sufficient conditions for solving
interactive consistency with $d$-faulty processes.}
\end{table}

The rest of the paper is organized as follows. Section 2 describes our system model and the agreement problems we study. In Section 3 (resp. Section 4) we prove a  tight bound for solving interactive consistency  with respect to oral messages (resp. signed messages). The consensus problem is discussed in Section 5. 
In Section 6, we show that the bounds on interactive consistency are similar if we also consider crash failures. 
We conclude the paper  in Section 7.

\input{model}

\input{IC-oral}

\input{IC-signed}

\input{consensus}

\input{crash-failure}

\input{conclusion}

\newpage

\bibliographystyle{abbrv}
\bibliography{ref}

\newpage
\appendix
\input{appendix}
\input{crash-appendix}

\end{document}
